Enhancement of SDR in Thessaloniki

### 2024-04-13 high_aod/GHI_enh_05_distributions.tex
Commit 2024-04-13 14:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-11}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# \_\_ Document options {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
[1] "Cloud" "Clear"
\end{verbatim}

\begin{verbatim}
 [1] "Exact_B.High_W.edir"  "Exact_B.High_W.edn"   "Exact_B.High_W.eup"  
 [4] "Exact_B.Low_2_W.edir" "Exact_B.Low_2_W.edn"  "Exact_B.Low_2_W.eup" 
 [7] "Exact_B.Exact_W.edir" "Exact_B.Exact_W.edn"  "Exact_B.Exact_W.eup" 
[10] "Exact_B.Low_W.edir"   "Exact_B.Low_W.edn"    "Exact_B.Low_W.eup"   
\end{verbatim}

\begin{verbatim}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  1.031   1.034   1.035   1.035   1.035   1.036 
\end{verbatim}

Alpha * HAU is CS\_ref

\hypertarget{using-criteria-enhanc_c_4-for-final-application}{%
\subsection{\texorpdfstring{Using criteria \textbf{Enhanc\_C\_4} for final application}{Using criteria Enhanc\_C\_4 for final application}}\label{using-criteria-enhanc_c_4-for-final-application}}

\hypertarget{use-tsi-as-reference-for-clear-sky.}{%
\subsection{1. Use TSI as reference for Clear sky.}\label{use-tsi-as-reference-for-clear-sky.}}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# \_\_ 1. My criteria  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\CommentTok{\# C1\_GLB\_ench\_THRES     \textless{}{-}  1.10 \#\# enchantment relative to HAU}
\NormalTok{C1\_GLB\_diff\_THRES     }\OtherTok{\textless{}{-}} \DecValTok{20}    \DocumentationTok{\#\# enchantment absolute diff to HAU}
\NormalTok{C1\_Clearness\_Kt\_THRES }\OtherTok{\textless{}{-}}  \FloatTok{0.8}  \DocumentationTok{\#\# enchantment threshold}
\CommentTok{\# C1\_wattGLB\_THRES      \textless{}{-} 20    \#\# minimum value to consider}

\NormalTok{DATA[, Enhanc\_C\_1 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}
\CommentTok{\# DATA[wattGLB           \textgreater{} CS\_ref * C1\_GLB\_ench\_THRES + C1\_GLB\_diff\_THRES \&}
\CommentTok{\#      ClearnessIndex\_kt \textgreater{} C1\_Clearness\_Kt\_THRES,}
\CommentTok{\#      Enhanc\_C\_1 := TRUE]}

\NormalTok{DATA[, Enhanc\_C\_1\_ref }\SpecialCharTok{:=}\NormalTok{ ETH }\SpecialCharTok{*}\NormalTok{ C1\_Clearness\_Kt\_THRES }\SpecialCharTok{+}\NormalTok{ C1\_GLB\_diff\_THRES]}
\NormalTok{DATA[wattGLB }\SpecialCharTok{\textgreater{}}\NormalTok{ Enhanc\_C\_1\_ref,}
\NormalTok{     Enhanc\_C\_1 }\SpecialCharTok{:=} \ConstantTok{TRUE}\NormalTok{]}

\ControlFlowTok{if}\NormalTok{ (SelEnhanc }\SpecialCharTok{==} \StringTok{"Enhanc\_C\_1"}\NormalTok{) \{}
\NormalTok{    DATA[ , GLB\_diff }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_1\_ref                    ] }\DocumentationTok{\#\# enhancement}
\NormalTok{    DATA[ , GLB\_ench }\SpecialCharTok{:=}\NormalTok{ ( wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_1\_ref ) }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_1\_ref ] }\DocumentationTok{\#\# relative enhancement}
\NormalTok{    DATA[ , GLB\_rati }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_1\_ref                    ]}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{use-tsi-as-reference-for-clear-sky.-1}{%
\subsection{2. Use TSI as reference for Clear sky.}\label{use-tsi-as-reference-for-clear-sky.-1}}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# \_\_ 2. Gueymard2017 Criteria  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\DocumentationTok{\#\# Clearness index \textgreater{} 0.8 / 1}
\NormalTok{C2\_Clearness\_Kt\_THRES }\OtherTok{\textless{}{-}} \FloatTok{0.8}
\NormalTok{DATA[, Enhanc\_C\_2 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}
\NormalTok{DATA[, Enhanc\_C\_2\_ref }\SpecialCharTok{:=}\NormalTok{ ETH }\SpecialCharTok{*}\NormalTok{ C2\_Clearness\_Kt\_THRES]}
\CommentTok{\# DATA[ClearnessIndex\_kt \textgreater{} C1\_Clearness\_Kt\_THRES,}
\CommentTok{\#      Enhanc\_C\_2 := TRUE]}
\NormalTok{DATA[wattGLB }\SpecialCharTok{\textgreater{}}\NormalTok{ Enhanc\_C\_2\_ref,}
\NormalTok{     Enhanc\_C\_2 }\SpecialCharTok{:=} \ConstantTok{TRUE}\NormalTok{]}

\ControlFlowTok{if}\NormalTok{ (SelEnhanc }\SpecialCharTok{==} \StringTok{"Enhanc\_C\_2"}\NormalTok{) \{}
\NormalTok{    DATA[ , GLB\_diff }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_2\_ref                    ] }\DocumentationTok{\#\# enhancement}
\NormalTok{    DATA[ , GLB\_ench }\SpecialCharTok{:=}\NormalTok{ ( wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_2\_ref ) }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_2\_ref ] }\DocumentationTok{\#\# relative enhancement}
\NormalTok{    DATA[ , GLB\_rati }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_2\_ref                    ]}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{use-haurwitz-as-reference-for-clear-sky.}{%
\subsection{3. Use Haurwitz as reference for Clear sky.}\label{use-haurwitz-as-reference-for-clear-sky.}}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# \_\_ 3. Vamvakas2020  Criteria  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\DocumentationTok{\#\# +5\% from model =\textgreater{} enhancements above 15 Wm\^{}2 the instrument uncertainty}
\NormalTok{C3\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}
\NormalTok{DATA[, Enhanc\_C\_3 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}
\NormalTok{DATA[, Enhanc\_C\_3\_ref }\SpecialCharTok{:=}\NormalTok{ CS\_ref }\SpecialCharTok{*}\NormalTok{ C3\_cs\_ref\_ratio]}
\NormalTok{DATA[wattGLB }\SpecialCharTok{\textgreater{}}\NormalTok{ Enhanc\_C\_3\_ref,}
\NormalTok{     Enhanc\_C\_3 }\SpecialCharTok{:=} \ConstantTok{TRUE}\NormalTok{]}

\ControlFlowTok{if}\NormalTok{ (SelEnhanc }\SpecialCharTok{==} \StringTok{"Enhanc\_C\_3"}\NormalTok{) \{}
\NormalTok{    DATA[ , GLB\_diff }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_3\_ref                    ] }\DocumentationTok{\#\# enhancement}
\NormalTok{    DATA[ , GLB\_ench }\SpecialCharTok{:=}\NormalTok{ ( wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_3\_ref ) }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_3\_ref ] }\DocumentationTok{\#\# relative enhancement}
\NormalTok{    DATA[ , GLB\_rati }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_3\_ref                    ]}
\NormalTok{\}}

\DocumentationTok{\#\# \_\_ 4. my Criteria  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}

\DocumentationTok{\#\# set values base}
\NormalTok{csmodel }\OtherTok{\textless{}{-}} \StringTok{"High\_B.Low\_W"}
\end{Highlighting}
\end{Shaded}

\hypertarget{use-libradtran-high_b.low_w-as-reference-for-clear-sky.}{%
\subsection{\texorpdfstring{4. Use libradtran \textbf{High\_B.Low\_W} as reference for Clear sky.}{4. Use libradtran High\_B.Low\_W as reference for Clear sky.}}\label{use-libradtran-high_b.low_w-as-reference-for-clear-sky.}}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{cat}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{ USING CSMODE:"}\NormalTok{, csmodel, }\StringTok{"}\SpecialCharTok{\textbackslash{}n\textbackslash{}n}\StringTok{"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}

 USING CSMODE: High_B.Low_W 
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{switch}\NormalTok{(csmodel,}
       \AttributeTok{Exact\_B.Exact\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.02}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{55}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_2\_B.Low\_2\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.03}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{5}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Exact\_W   =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.04}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.High\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.11}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.31}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
\NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
\DocumentationTok{\#\# init flag}
\NormalTok{DATA[, Enhanc\_C\_4 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}

\CommentTok{\# DATA[, max(SZA)]}

\NormalTok{smo }\OtherTok{\textless{}{-}} \FunctionTok{approxfun}\NormalTok{(}
    \AttributeTok{x =} \FunctionTok{c}\NormalTok{(}\DecValTok{90} \SpecialCharTok{{-}}\NormalTok{ BIO\_ELEVA, C4\_lowcut\_sza  ),}
    \AttributeTok{y =} \FunctionTok{c}\NormalTok{(C4\_lowcut\_ratio,  C4\_cs\_ref\_ratio)}
\NormalTok{    )}

\FunctionTok{smo}\NormalTok{(}\DecValTok{80}\SpecialCharTok{:}\DecValTok{70}\NormalTok{) }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{/}\FunctionTok{cosd}\NormalTok{(}\DecValTok{80}\SpecialCharTok{:}\DecValTok{70}\NormalTok{) }\SpecialCharTok{/} \FunctionTok{max}\NormalTok{(}\DecValTok{1}\SpecialCharTok{/}\FunctionTok{cosd}\NormalTok{(}\DecValTok{80}\SpecialCharTok{:}\DecValTok{70}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
 [1]        NA        NA 1.0941141 1.0026612 0.9243490 0.8565476 0.7972846
 [8] 0.7450515 0.6986754 0.6572300 0.6199744
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{cat}\NormalTok{(}\StringTok{"C4 factor:"}\NormalTok{, C4\_cs\_ref\_ratio,   }\StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
C4 factor: 1.11 
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{cat}\NormalTok{(}\StringTok{"C4 offset:"}\NormalTok{, C4\_GLB\_diff\_THRES, }\StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
C4 offset: 0 
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# \_\_\_\_ Create global irradiance W/m\^{}2  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\NormalTok{DATA[, }\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{) }\SpecialCharTok{:=}\NormalTok{ (}\FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".edir"}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".edn"}\NormalTok{))) }\SpecialCharTok{/} \DecValTok{1000}\NormalTok{ ]}

\DocumentationTok{\#\# \_\_\_\_ Apply sun{-}earth distance correction  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\NormalTok{DATA[, }\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{) }\SpecialCharTok{:=} \FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) }\SpecialCharTok{/}\NormalTok{ sun\_dist}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{ ]}

\DocumentationTok{\#\# \_\_\_\_ Apply adjustment to Kurudz spectrum  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\NormalTok{DATA[, }\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{) }\SpecialCharTok{:=} \FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) }\SpecialCharTok{*}\NormalTok{ TSI\_Kurudz\_factor ]}

\DocumentationTok{\#\# \_\_\_\_ Calculate clearness index  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\NormalTok{DATA[, ClearnessIndex\_C\_4 }\SpecialCharTok{:=}\NormalTok{ wattGLB }\SpecialCharTok{/} \FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) ]}

\FunctionTok{hist}\NormalTok{(DATA}\SpecialCharTok{$}\NormalTok{ClearnessIndex\_C\_4, }\AttributeTok{breaks =} \DecValTok{100}\NormalTok{)}
\FunctionTok{abline}\NormalTok{(}\AttributeTok{v =}\NormalTok{ C4\_cs\_ref\_ratio, }\AttributeTok{col =} \StringTok{"red"}\NormalTok{ )}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-10-1} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# \_\_\_\_ Calculate reference and mark data  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\DocumentationTok{\#\# for most of the data}
\NormalTok{DATA[SZA }\SpecialCharTok{\textless{}}\NormalTok{ C4\_lowcut\_sza, Enhanc\_C\_4\_ref }\SpecialCharTok{:=}\NormalTok{ (}\FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) }\SpecialCharTok{*}\NormalTok{ C4\_cs\_ref\_ratio) }\SpecialCharTok{+}\NormalTok{ C4\_GLB\_diff\_THRES ]}
\DocumentationTok{\#\# fol low sun angles}
\CommentTok{\# DATA[SZA \textgreater{} C4\_lowcut\_sza, Enhanc\_C\_4\_ref := (get(paste0(csmodel,".glo")) * C4\_lowcut\_ratio) ]}
\NormalTok{DATA[SZA }\SpecialCharTok{\textgreater{}}\NormalTok{ C4\_lowcut\_sza, Enhanc\_C\_4\_ref }\SpecialCharTok{:=}\NormalTok{ (}\FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) }\SpecialCharTok{*} \FunctionTok{smo}\NormalTok{(SZA)) ]}

\NormalTok{DATA[wattGLB }\SpecialCharTok{\textgreater{}}\NormalTok{ Enhanc\_C\_4\_ref ,}
\NormalTok{     Enhanc\_C\_4 }\SpecialCharTok{:=} \ConstantTok{TRUE}\NormalTok{]}
\DocumentationTok{\#\# use threshold to compute values}
\ControlFlowTok{if}\NormalTok{ (SelEnhanc }\SpecialCharTok{==} \StringTok{"Enhanc\_C\_4"}\NormalTok{) \{}
\NormalTok{    DATA[ , GLB\_diff }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_4\_ref                    ] }\DocumentationTok{\#\# enhancement}
\NormalTok{    DATA[ , GLB\_ench }\SpecialCharTok{:=}\NormalTok{ ( wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_4\_ref ) }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_4\_ref ] }\DocumentationTok{\#\# relative enhancement}
\NormalTok{    DATA[ , GLB\_rati }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_4\_ref                    ]}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

\hypertarget{using-creteria-enhanc_c_4}{%
\section{Using creteria: Enhanc\_C\_4}\label{using-creteria-enhanc_c_4}}

\hypertarget{distribution-of-different-metrics}{%
\section{Distribution of different metrics}\label{distribution-of-different-metrics}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-3} \end{center}

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_1}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
6082440 & 119727 \\
\end{longtable}

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_2}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
6012875 & 189292 \\
\end{longtable}

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_3}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
5455724 & 746443 \\
\end{longtable}

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_4}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
6072539 & 129628 \\
\end{longtable}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-27} \end{center}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-13}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Reference mode:       High_B.Low_W 
\end{verbatim}

\begin{verbatim}
Enhancemnet criteria: Enhanc_C_4 
\end{verbatim}

@@

\hypertarget{frequency-distributions}{%
\subsubsection{Frequency Distributions}\label{frequency-distributions}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/freqdistributions-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/freqdistributions-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/freqdistributions-3} \end{center}
